non_phylo_analyses

### 2018-04-07 reports/non_phylo_model.Rmd
changing the location in which we choose the traits to use, and switching that from the trait funxs script to the model report(s).

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-inner_join(response_variables,traits)
```

>>>>

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-left_join(traits,response_variables, by="binom") %>%
  filter(SCIENTIFIC_NAME_tree != "not_treated_as_species") %>%
  # drop columns that we aren't inerested in
  select(-brain_size)
```
